### 2017-10-03 Sections/quantum_genetic_medicine.tex
Quantum simulation update

@@

\begin{figure}[!htb]
	\includegraphics[width=0.55\columnwidth]{genetic_medicine_pipeline}
	\caption{Pipeline for quantum-enhanced genetic drug development.} \label{fig:genetic_med_pipe}
\end{figure}

>>>>

\comment{Add subsections for each of the subroutines/oracles}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.5\columnwidth]{genetic_medicine_pipeline}
	\caption{Pipeline for quantum-enhanced genetic drug development. A quantum search algorithm searches over algorithmically-generated drug compounds, for each performing Hamiltonian simulation, to determine if the compound's score is above a threshold. The quantum search subroutine yields a quadratic enhancement in the number of drugs that can be simulated in parallel, and the Hamiltonian simulation subroutine yields an exponential enhancement over classical simulation techniques.} \label{fig:genetic_med_pipe}
\end{figure}
